Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-17 paper/method.tex
Update graphics.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
\caption{Merge error detection: Potential borders are generated on inverted images by randomly placing watershed seeds (green) on the boundary of a dilated segment. The best ranked seeds and border (both in red) result in the shown error correction.}
%Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
\caption{Merge error detection: Potential borders are generated using inverted images by randomly placing watershed seeds (green) on the boundary of a dilated segment. The best ranked seeds and border (both in red) result in the shown error correction.}
%Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}
